\begin{acknowledgments}

This dissertation represents a work that required effort from a lot of different people in many different ways. The list of people includes but is not limited to CMS and UNL colleagues from all over the world, family and friends.

Specifically, first, I would like to thank my advisor Ilya Kravchenko for his help and support throughout my whole experience as a PhD student at UNL, from the admission process and to the process of writing this dissertation. We discussed every single step of the $W\gamma$ measurements, and I could always rely on getting a guidance and valuable advice whether it is an issue in a measurement step, technical question or effective collaboration with CMS colleagues. Under Ilya's supervision, I raised from a first year graduate student who can only complete certain very specific tasks to a researcher who can complete her own project and get it endorsed for the PhD defense. Overall, the list of CMS colleagues who made direct contribution to the $W\gamma$ measurement and/or provided a good number meaningful recommendations starts from Yurii Maravin, Lovedeep Saini, Joshua Kunkle, Senka Duric, Kuo Chia-Ming, Sachiko Toda McBride, Yutaro Iiyama, and never ends.   

Additionally,  I would like to express my deep gratitude Frank Meier for supervising another part of my work, the alignment of the CMS tracking system and to make my contribution to the performance of the CMS experiment. We spent hours discussing alignment algorithms, various technical tools, and results. Frank helped me to get involved in the project, get trained and tremendously improve in the level of understanding and capabilities. My work in the tracker alignment group was a very integrated team work, where it is very difficult to separate your contribution from the contributions of others. The list of colleagues who made our collaboration so fruitful, besides Frank, includes Marco Musich, Matthias Schr\"{o}der, Tapio Lampen, Patrick Connor, Nazar Stephaniuk, Candice You and many others. 

I would like to thank UNL professors Ken Bloom, Brad Schadwick and Glenn Ledder for their time spent on serving as my graduate committee and providing set of questions and comments regarding the dissertation. Ken Bloom also, alongside with other UNLHEP professors, postdocs and students, participated in tricky discussions regarding various aspects of my research work during our group meetings as well as during individual meetings and over e-mails. 

Finally, a special thanks to my parents Elena Tsukanova and Grigory Tsukanov, to my husband Sergey Avdeev, and to my daughters Oksana and Yana Avdeeva for being a source of support in my life and research career, for their constant patience and understanding. Family support has meant a lot to me, and these people's effect on any aspect of my personality cannot be overestimated.



\end{acknowledgments}
