\chapter{Summary and Conclusions}
\label{sec:Conclusions}

This dissertation reports a measurement of the total and differential cross sections, $\sigma$ and $\frac{d\sigma}{dP_T^{\gamma}}$, of the $W\gamma$ production in the muon and the electron channels using full~2012 dataset of $L=$19.6~fb$^{-1}$ collected by CMS at $\sqrt{s}=$8~TeV. This is the first measurement of the differential cross section of the $W\gamma$ production at the CMS experiment. The results are in agreement between two channels and also agree with the predictions computed at NLO using the MCFM program and the Madgraph~5 Monte Carlo generator. The agreement with theory means agreement with the MC predictions with no clear indication of new physics.

The differential cross section measurement has the special significance because a new physics would be difficult to detect in the total production cross section, however accurate measurement of the differential cross section with respect to an observable kinematic variable of the final state particles, and especially with respect to the $P_T^{\gamma}$, are sensitive probes to BSM models. The results of the differential spectrum measurement could be used to set limits on aTGC constants.

In addition to $W\gamma$ cross section, we also measure $Z\gamma$ cross section and compare results with the published $Z\gamma$ CMS measurement at $\sqrt{s}=$8~TeV. The good agreement between our and published results on $Z\gamma$ cross section validates parts of our $W\gamma$ measurement that are the same between $Z\gamma$ and $W\gamma$ measurements including lepton and photon selection, jets$\rightarrow\gamma$ background estimation, detector resolution unfolding, acceptance and efficiency corrections.

Measurements of $W\gamma$ and the other diboson and triboson productions at higher energies and luminosities will have more opportunities to discover a new physics if it is present. That is one of the reasons why these measurements remain a significant part of CMS physics program for studies at $\sqrt{s}=$13~TeV.

%  \begin{itemize}
%     \item Cross section for muon and electron channels are computed 
%     \item This is the first measurement of the differential $W\gamma$ cross section with CMS
%     \item Results agree with the MC prediction
%     \item Results between the two channels agree
%     \item Relative systematic uncertainties on total cross section are larger than those reported by the CMS 7 TeV measurement
%     \item Good agreement in the $Z\gamma$ check validates most parts of the analysis (those which are the same for the muon and electron channels)
%  \end{itemize}
