\chapter{Introduction}
\label{sec:intro}

Elementary particle physics describes fundamental particles and their interactions. Fundamental particles are the smallest constituents of our Universe. When examined at smaller scales, the substances around us consist of molecules, molecules consist of atoms. In an atom there is a nucleus made of neutrons and protons and some number of electrons occupying orbits around the nucleus. Protons and neutrons have a structure while an electron is not known to have any internal structure, therefore, an electron is an example of a particle which is considered to be fundamental.

Interactions of elementary particles are described by quantum field theories which incorporate principles of the quantum mechanics and the special theory of relativity. The set of such theories, including quantum elecrtrodynamics (QED), quantum chromodynamics (QCD) and the theory of weak interactions is called the Standard Model (SM). Current observations have proved the SM to be an accurate description of elementary particle interactions.  

However, there are several experimental observations that are not described by the SM such as effects of gravity, dark matter, dark energy, matter/antimatter asymmetry and others. Therefore, the SM is not a complete theory of particle interactions. There are several SM extensions offered by theorists as well as radically new theories waiting for experimental confirmation or exclusion. 

Some SM extensions and new theories predict the existence of heavy particles with masses lying beyond experimentally reachable energies. The search of these particles is a priority in particle physics. One source of highly energetic elementary particles is cosmic rays. The most energetic particles ever observed came from this source. However, cosmic rays are totally uncontrollable and such highly energetic particles are rare. If we want to produce a large number of particles in a given energy range, we need to use a particle accelerator. A large amount of data allows experimentalists to perform a statistical analysis and increase the probability of finding a new particle if it exists.

Symmetric colliding beams is the most effective way to produce as heavy particles as possible given the energies of the colliding particles. Compared to experiments colliding a single beam at a fixed target, in the case of a symmetric collision the total momentum of two colliding particles is zero and, therefore, much larger fraction of energy can transfer to a mass of a new particle.  The Large Hadron Collider (LHC) is one such collider with the highest energy in the world. It can produce the most massive particles to probe physics beyond the SM (BSM). 
%It collides two proton ($pp$) beams, two lead ion beams ($Pb-Pb$) or a proton beam to a lead ion beam ($p-Pb$). The design energies for a colliding proton and a colliding lead ion at LHC are~7~TeV and~522~TeV respectively. \\

The Compact Muon Solenoid (CMS) is one of two general-purpose detectors at the LHC. It is placed at one of four collision points. CMS has a broad physics program including searches for the BSM physics as well as the precision measurements of the parameters of the SM itself. The measurement of this dissertation is a SM measurement with CMS data collected in~2012 in proton-proton ($pp$) collisions of LHC with beam energies of~4~TeV. The result can be compared to the SM prediction. Certain BSM theories predict a deviation of the result of this measurement from its SM value, therefore, with this measurement, in addition to testing the SM, we also search for a new physics.

%In this dissertation, the study of $pp\rightarrow W\gamma + X$ process where the $W$ decays as $W\to \ell\nu$ where $\ell = e, \mu$ is reported. The $W\gamma$ production with leptonic $W$ decays proceeds through one of the following three processes: the initial state radiation where a photon is emitted from one of the incoming partons, the final state radiation where a photon is radiated off the charged lepton from the $W$ boson decay, and, finally, the triple gauge coupling (TGC) where a photon is emitted from the $W$ boson. Many BSM theories predict an enchancement of the TGC production over the SM value and, therefore, the experimental search for such an enchancement is a good test for such theories.\\ 
%The total and the differential cross section with respect to the photon transverse momentum ($P_T^\gamma$) has been measured. The $P_T^{\gamma}$ is sensitive to the potential anomalous TGC (aTGC) in the high $P_T^{\gamma}$ region. The disagreement between the measured and theoretically predicted differential cross section at the higher $P_T^{\gamma}$ end would be an indication of the possible presence of the aTGC. \\

The rest of this chapter gives general introductory information about the SM while Ch.~\ref{sec:WgAbout} concentrates on the theory of the SM and BSM $W\gamma$ production and also discusses previous measurements of this process. Chapter~\ref{sec:Exp} describes LHC and CMS in more details. Chapter~\ref{sec:alignment} explains one specific detail of the CMS operation that is the spacial alignment of the tracking detector of charged particles. Finally, Ch.~\ref{sec:AN_WgMeas} describes the details of the measurement of this dissertation and reports the results. 

%\include{Intro_FundParticles}
%\include{Intro_Electroweak}
%\include{Intro_Higgs}
%\include{Intro_QCD}
%\include{Intro_ppCollisions}
%\include{Intro_OpenQuestions}
