\section{Introduction}
\label{sec:intro}


Elementary particle physics describes our world in terms of its smallest constituents, fundamental particles, and their interactions. Going from larger to smaller scales, substances around us consist of molecules, molecules consist of atoms, in an atom, there is a nucleus made of neutrons and protons and some number of electrons occupying their orbits around the nucleus. Protons and neutrons have a structure while an electron is not known to have any structure, therefore, an electron is an example of a particle which is considered to be fundamental.\\

Interactions of elementary particles are described by quantum field theories which incorporate principles of the quantum mechanics and the special theory of relativity. The set of such theories, including quantum elecrtrodynamics (QED), quantum chromodynamics (QCD) and the theory of weak interactions is called the Standard Model (SM). It has been proven to be an accurate description of interactions of elementary particles observed by now.\\ 

However, there are several experimental observations which are not described by the SM such as gravity, dark matter, dark energy, matter/antimatter asymmetry and others. Therefore, the SM is not the complete theory of particle interactions. There are several SM extensions offered by theorists as well as radically new theories waiting for the experimental confirmation or disproof. \\

Some SM extensions and new theories predict the existence of heavy particles mass of which possibly lies beyond experimentally reachable energies. The search of these particles is one of the prioritized directions in particle physics. One source of highly energetic elementary particles is cosmic rays. The most energetic particles ever observed came from this source. However, cosmic rays are totally uncontrollable and such highly energetic particles are rare. If we want to produce a large number of particles in a given energy range, we need to use a particle accelerator. A large amount of data allows experimentalists to perform a statistical analysis and increase the probability to find a new particle if it exists.\\

Symmetric colliding beams is the most effective way to produce as heavy particles as possible given the energies of the colliding particles. Comparing to experiments of colliding a single beam to a fixed target, in case of a symmetric collision the total momentum of two colliding particles is zero and, therefore, much larger fraction of energy can transfer to a mass of a new particle.  The Large Hadron Collider (LHC) is such a collider with the highest energy in the world ever built. It can produce the most massive particles to probe physics beyond the SM. It collides two proton ($pp$) beams, two lead ion beams ($Pb-Pb$) or a proton beam to a lead ion beam ($p-Pb$). The design energies for a colliding proton and a colliding lead ion at LHC are~7~TeV and~522~TeV respectively. \\

Compact Muon Solenoid (CMS) is one of two general-purpose detectors at the LHC. It is placed at one of six collision points. CMS has a wide physics program including searches for the beyond SM (BSM) physics as well as the precision measurements of the SM parameters themselves.\\

%In this dissertation the analysis of $pp\rightarrow W\gamma + X$  processes using  leptonic decays of $W\to \ell\nu$ where $\ell = e, \mu$ is reported. The $W\gamma$ productions with leptonic $W$ decays can go through one of the following three processes: initial state radiation where a photon is produced from one of the incoming partons, final state radiation where a photon is radiated off the charged lepton from the $W$ boson decay, and finally when a photon is produced via the triple gauge coupling (TGC) where a photon is emitted from the $W$ boson. \\ 

%To search for the deviations from the SM, one would search for an anomalous TGC which would be indicated by the enhance of the TGC production over the SM prediction. \\

The total and the differential cross section with respect to the photon transverse momentum ($P_T^\gamma$) has been measured. The $P_T^{\gamma}$ is sensitive to the potential anomalous TGC (aTGC) in the high $P_T^{\gamma}$ region. The disagreement between the measured and theoretically predicted differential cross section at the higher $P_T^{\gamma}$ end would be an indication of the possible presence of the aTGC. \\

The rest of this chapter gives general introductory information about the SM while chapter \ref{sec:WgAbout} concentrates on the theory of the SM and BSM $W\gamma$ production and also discusses previous measurements of this process. Chapter \ref{sec:Exp} describes LHC and CMS in more details. Chapter \ref{sec:alignment} explaines on specific aspect of the CMS operation which is the tracker alignment. Finally, chapter \ref{sec:AN_WgMeas} describes the details of the measurement of this dissertation and reports the results.\\ 



%\include{Intro_FundParticles}
%\include{Intro_Electroweak}
%\include{Intro_Higgs}
%\include{Intro_QCD}
%\include{Intro_ppCollisions}
%\include{Intro_OpenQuestions}
